NoTitle

### 2017-06-13 Aplas17/sections/Introduction.tex
add a ref

A reason why programming languages have resisted to multiple
inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
multiple inheritance is good but ``\emph{there is no good way to do it}''.
One of the most sensitive and critical issues is perhaps the ambiguity
introduced by multiple inheritance. One case is the famous
\textit{diamond problem}~\cite{Sak89dis,Singh1995}. In the diamond problem inheritance could allow
one feature to be inherited from multiple parent classes, hence
conflicts arise. The variety of strategies on resolving such conflicts
urges the occurrence of different multiple inheritance models,
including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
languages have taken care of this case intensively. Other issues
include how multiple inheritance deals with state, as discussed in
which also has been discussed quite extensively~\cite{classless, C++,...}.

>>>>

A reason why programming languages have resisted to multiple
inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
multiple inheritance is good but ``\emph{there is no good way to do it}''.
One of the most sensitive and critical issues is perhaps the ambiguity
introduced by multiple inheritance. One case is the famous
\textit{diamond problem}~\cite{Sak89dis,Singh1995}. In the diamond problem inheritance could allow
one feature to be inherited from multiple parent classes, hence
conflicts arise. The variety of strategies on resolving such conflicts
urges the occurrence of different multiple inheritance models,
including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
languages have taken care of this case intensively. Other issues
include how multiple inheritance deals with state, as discussed in
which also has been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.
